Towards a free/open-source universal-dependency treebank for Kazakh

### 2015-06-20 2015-turklang-kazdep/paper.tex
hargle
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60910 72bbbca6-d526-0410-a7d9-f06f51895060

As an agglutinative language with rich morphology and agreement phenomena, Kazakh presents some interesting challenges for computational syntax.  These challenges include the syntactic functions of the various ``case'' morphemes, problems of ``zero derivation'', non-finite clauses,       These decisions include how the relations ``case'' morphemes create between syntactic elements work, as well as a number of processes of ``zero derivation''.A morphological transducer has already been designed \parencite{Washington14}, which implements a number of decisions about how various inflectional morphemes affect the part of speech and syntactic function of various word forms.

>>>>

As an agglutinative language with rich morphology and agreement phenomena, Kazakh presents some interesting challenges for computational syntax.  These challenges include the syntactic functions of the various ``case'' morphemes, problems of ``zero derivation'', non-finite clauses, and copulas and copula constructions.  An existing morphological transducer of Kazakh \parencite{Washington14} implements analyses of how these various phenomena occur on the morphological level.  These phenomena will be described in this section, and how they were dealt with in the annotation of the treebank will be described in section~\ref{sec:annotation}.
